\textbf{{\Large {Recurrent relation for branching coefficients of affine Lie algebras}}}

### 2009-11-24 AffineLieAlgebras/InformalNotes/article.tex
Some work on the physical example of the affine branching and on the new implementation in Scheme.

\begin{comment}
  Do the calculation, show the restriction on the grade and the final result
  \begin{equation}
    \label{eq:35}
    Z=\left|\chi_{[10,0]}+\chi_{[4,6]}\right|^2+\left|\chi_{[7,3]}+\chi_{[3,7]}\right|^2+\left|\chi_{[6,4]}+\chi_{[0,10]}\right|^2
  \end{equation}
\end{comment}

>>>>

This affine embedding is the affine extension of the special embedding $A_1\subset C_2$ with the embedding index equal to 10. The projection of the weights of algebra $C_2$ is calculated using the projection matrix $\mathcal{P}=(3,4)$. The embedding index
\begin{equation}
  \label{eq:37}
  x_e=\frac{\left|\mathcal{P}\Theta_{\mathfrak{g}}\right|^2}{\left|\Theta_{\mathfrak{a}}\right|^2}=\frac{k_{\mathfrak{a}}}{k_{\mathfrak{g}}}=10
\end{equation}
If we consider this embedding in the orthogonal basis where the simple roots of $C_2$ are given by
\begin{equation}
  \label{eq:38}
  \alpha_1=(1,-1),\quad \alpha_2=(0,2),
\end{equation}
then the simple root of the embedded $A_1$ is equal to
\begin{equation}
  \label{eq:39}
  \beta=\sqrt{\frac{2}{5}}(3,1)
\end{equation}
It is easy to see that the set $\Delta_{\bot}$ of the $C_2$ roots orthogonal to $\beta$ is empty.

Now we proceed the computation of the branching coefficients using the algorithm \ref{sec:algorithm}. 
On the level 1 there exist three dominant weights with Dynkin labels $[1,0,0], \; [0,1,0],\; [0,0,1]$.
\begin{comment}
  Do the calculation, show the restriction on the grade and the final result
  \begin{equation}
    \label{eq:35}
    Z=\left|\chi_{[10,0]}+\chi_{[4,6]}\right|^2+\left|\chi_{[7,3]}+\chi_{[3,7]}\right|^2+\left|\chi_{[6,4]}+\chi_{[0,10]}\right|^2
  \end{equation}
\end{comment}
